---
format: gfm
---

## Reading in the Data

The code below shows the code I used to read in the data, where each song is its own csv file. I then created columns for the metadata associated with each song. 

```{r}
#reading in packages I will need
library(tidyverse)
library(dplyr)
library(stringr)
library(tidytext)
 library(stringr)

#reading multiple files of data into R
lyrics <- list.files(pattern=".csv") |>
  read_csv(id = "file")

# Putting each song's metadata in separate columns
lyrics$track_type = str_extract(lyrics$file, "Title|Nontitle")
lyrics$album_year_20XX = str_extract(lyrics$file, "15|20|23|24")
# Can't quite get the song title to work right now
#lyrics$song_title = str_extract(lyrics$file, "")
lyrics

```

## Cleaning up the Data

I used functions from tidy text to make it so that each word is its own row.

```{r}

lyrics |>
 unnest_tokens(word, "Lyrics") |> arrange(desc(album_year_20XX)) -> withlang
print(withlang)

#creating vector with only the lyrics in single-word rows
select(withlang, "word") -> withlang
print(withlang)


#mutating withlang to detect language of rows of lyrics
withlang <- withlang %>%
  mutate(
    word   = as.character(word),
    korean  = str_detect(word, "[가-힣]"),
    english = str_detect(word, "[A-Za-z]")
  )

print(withlang)

```



## Analyzing the Data

I will use language-detecting functions to label the individual words as English, Korean, or Other. 


```{r}



```






Session Info
```{r}
sessionInfo()
```



